Usage metrics

### 2020-12-21 analysis/usage.Rmd
minor

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/
  calls_path: base/summarized.fst
  corpus_path: corpus.fst
  static_path: package-evals-static.csv
  force_rebuild: TRUE
---

@@

base_dir <- params$base_dir
calls_path <- paste0(base_dir, params$calls_path)
corpus_path <- paste0(base_dir, params$corpus_path)
static_path <- paste0(base_dir, params$static_path)
```

@@

rebuild <- TRUE
# We only read the orignal evals_calls file if we don't have a summarized
# version stored on disk.  NOTE: the heuristic to detect changes is file
# size. If that fails, manually delete `.lock.fst`
if (file.exists("Data/.lock.fst")) {
  saved <- read.fst("Data/.lock.fst")[[1,1]]
  if (saved == file.size(calls_path)) {
    read.fst("Data/E.fst") %>% as_tibble() -> E
    rebuild <- FALSE
  }
}
if (params$force_rebuild | rebuild) {
  read_fst(calls_path) %>% as_tibble() -> E_raw

@@

We recorded `r nb_calls` to eval, out of these, there were `r evalq_calls`
(`r fmt(ratio(evalq_calls,nb_calls))`) calls to `evalq`, `r eval.parent_calls` 
(`r fmt(ratio(evalq_calls,nb_calls))`) calls to `eval.parent`,  and
`r local_calls` (`r fmt(ratio(evalq_calls,nb_calls))`) calls to `local`.

@@

```{r eval-calls-violin-plot, include=F}
sites_per_package %>%
  ggplot(aes(x = "", y = n, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  labs(y = "Eval calls per package") +
  theme(legend.position = "none") -> G

@@

```{r include=F}
lbl_colour <- rep("black", 11)
lbl_colour[[4]] <- "transparent"
E %>%
  ggplot(aes(x = ast_nodes, weight = duplicates)) +
  stat_density(aes(y = ..count..), color = "black", fill = "blue", alpha = 0.3) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 10, 30, 100, 300, 1000), trans = "log1p", expand = c(0, 0)) +
  labs(x = "Size (nodes)") +
  theme(text = element_text(size=17),
        axis.text.x = element_text(color = lbl_colour)) -> G

E %>% 
  filter(ast_nodes < 25) %>%
  ggplot(aes(x = ast_nodes, weight = duplicates)) +
  geom_histogram(binwidth = 1, color = "black", fill = "blue", alpha = 0.3) +
  scale_y_continuous(labels = comma) +
  labs(x = "nodes") +
  theme(text = element_text(size=17),  panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), aspect.ratio = 4/3) -> GG

@@

```{r include=F}
E %>%
  filter(opcodes > 50) %>%
  ggplot(aes(x = "", y = opcodes), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1, fill = "blue", alpha = 0.3) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "", x = "") +
  theme(legend.position = "none", text = element_text(size=25)) -> G

@@

```{r include=F}
E %>%
  filter(opcodes > 0) %>% # == 0 if from eval.parent, because we do not count eval loops for it
  filter(opcodes <= 50) %>%
  ggplot(aes(x = "", y = opcodes), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7, fill = "blue", alpha = 0.3) +
  labs(y = "Instructions", x = "") +
  theme(legend.position = "none", text = element_text(size=25)) -> G

@@

```{r loops, include=FALSE}
# Which call sites where exercised and how many times, per run.
exercised <- E %>%
  group_by(file) %>% # group by runs
  count(src_ref, wt = duplicates) # weigh by duplicates

@@

# Plot the low trigger counts...
triggered %>%
  filter(average < 50) %>%
  ggplot(aes(x = average)) +
  geom_histogram(binwidth = 1, fill = "blue", alpha = 0.3, colour = "black") +
  theme(text = element_text(size=16), axis.text = element_text(size=20), aspect.ratio = 4/3) -> G

@@

```{r type-diversity, include=F}
E %>%
  ggplot(aes(x = fct_rev(fct_infreq(type)), weight=duplicates)) +
  geom_bar() +
  coord_flip() +
  labs(x = "type") -> G

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/
  calls_path: package/summarized.fst
  corpus_path: corpus.fst
  static_path: package-evals-static.csv
  force_rebuild: FALSE
---

@@

calls_path <- paste0(params$base_dir, params$calls_path)
corpus_path <- paste0(params$base_dir, params$corpus_path)
static_path <- paste0(params$base_dir, params$static_path)
```

@@

rebuild <- TRUE
# We only read the file if we don't have our summarized file on disk.
# To force reading, set the force_rebuild parameter to true.
if (file.exists("Data/.lock.fst")) {
  saved <- read.fst("Data/.lock.fst")[[1,1]]
  if (saved == file.size(calls_path)) {
    read.fst("Data/E.fst") %>% as_tibble() -> E
    rebuild <- FALSE
  }
}
if (params$force_rebuild | rebuild) {
  read_fst(calls_path) %>% as_tibble() -> E_raw

@@

We recorded `r nb_calls` to eval, out of these, there were `r evalq_calls`
(`r fmt(ratio(evalq_calls,nb_calls))`) calls to `evalq`, `r eval.parent_calls` 
(`r fmt(ratio(eval.parent_calls,nb_calls))`) calls to `eval.parent`,  and
`r local_calls` (`r fmt(ratio(local_calls,nb_calls))`) calls to `local`.

@@

```{r eval-calls-violin-plot}
sites_per_package %>%
  ggplot(aes(x = "", y = n, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  labs(y = "Eval calls per package") +
  theme(legend.position = "none")

@@

```{r echo=FALSE}
lbl_colour <- rep("black", 11)
lbl_colour[[4]] <- "transparent"
E %>%
  ggplot(aes(x = ast_nodes, weight = duplicates)) +
  stat_density(aes(y = ..count..), color = "black", fill = "blue", alpha = 0.3) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 10, 30, 100, 300, 1000), trans = "log1p", expand = c(0, 0)) +
  labs(x = "Size (nodes)") +
  theme(text = element_text(size=17),
        axis.text.x = element_text(color = lbl_colour))

E %>% 
  filter(ast_nodes < 25) %>%
  ggplot(aes(x = ast_nodes, weight = duplicates)) +
  geom_histogram(binwidth = 1, color = "black", fill = "blue", alpha = 0.3) +
  scale_y_continuous(labels = comma) +
  labs(x = "nodes") +
  theme(text = element_text(size=17),  panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), aspect.ratio = 4/3)

@@

```{r echo=FALSE}
E %>%
  filter(opcodes > 50) %>%
  ggplot(aes(x = "", y = opcodes), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1, fill = "blue", alpha = 0.3) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "", x = "") +
  theme(legend.position = "none", text = element_text(size=25))

@@

```{r echo=FALSE}
E %>%
  filter(opcodes > 0) %>% # == 0 if from eval.parent, because we do not count eval loops for it
  filter(opcodes <= 50) %>%
  ggplot(aes(x = "", y = opcodes), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7, fill = "blue", alpha = 0.3) +
  labs(y = "Instructions", x = "") +
  theme(legend.position = "none", text = element_text(size=25))

@@

```{r loops, echo=FALSE}
# Which call sites where exercised and how many times, per run.
exercised <- E %>%
  group_by(file) %>% # group by runs
  count(src_ref, wt = duplicates) # weigh by duplicates

@@

# Plot the low trigger counts...
triggered %>%
  filter(average < 50) %>%
  ggplot(aes(x = average)) +
  geom_histogram(binwidth = 1, fill = "blue", alpha = 0.3, colour = "black") +
  theme(text = element_text(size=16), 
        axis.text = element_text(size=20), 
        aspect.ratio = 4/3)

@@

```{r type-diversity, echo=FALSE}
E %>%
  ggplot(aes(x = fct_rev(fct_infreq(type)), weight=duplicates)) +
  geom_bar() +
  coord_flip() +
  labs(x = "type")
